\documentclass[12pt]{ctexart}
\usepackage{geometry}
\usepackage{pifont}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\begin{document}
\huge Unit 1 \\
\begin{center}
\LARGE Text 1-1
\end{center}

\large
\par In it's 4.5 billion years, Earth has evolved from its hot, violent birth to the celebrated watery blue planet that stands out in pictures from space. But in a new book, two noted University of Washington astrobiologists say the planet already has begun the long process of developing into a burned-out cinder, eventually to be swallowed by the sun.
\par By their reckoning, Earth's ``day in the sun" has reached 4:30 a.m., correspoding to its 4.5 billion-year age. By 5 a.m., the 1 billion-year reign of animals and plants will come to an end. At 8 a.m. the oceans will vaporize. At noon--after 12 billion years--the ever-expanding sun, transformed into a red giant, will engulf the planet, melting away any evidence it ever existed and sending molecules and atoms that once were Earth floating off into space.
\par ``The disappearance of our planet is still 7.5 billion years away, but people really should consider the fate of our world and have a realistic understanding of where we are going," said UW astrophysicist Donald Brownlee. ``We live in a fabulous place at a fabulous time. It's a healthy thing for people to realise what a treasure this is in space and time, and fully appreciate and protect their environment as much as possible."
\par The prospects of humans surviving by moving to some other habitable planet or moon aren't good, Brownlee and Ward contend, because even if such a place were found, getting there would be a huge obstacle. Various probes sent into space could survive Earth's demise, and just a few grams of material could arguably carry a DNA sample from every human, they say, but it's not likely the human species itself will survive. Long before the planet's final end, life will become quite chanllenging, and finally impossible, for humans.
\par As the sun get hotter and grows in size, it will envelop Mercury and Venus. It is possible it will stop just short of Earth, the authors say, but the conditions still would make this a most-inhospitable planet. More likely, though, the sun will consume Earth as well, severing all the chemical bonds between molecules and sending its individual atoms into space, pherhaps eventually to form new planets. That would leave Mars as the nearest planet to the sun, and on Mars the fading sun's glow would be like that of Earth's moon.
\par That end is still some 7.5 billion years distant, but by then Earth will have faced a variety of ``ends" along the way, the authors say. The last dinosaur perished long ago. Still to come are the last elephant, the last tree, the last flower, the last glacier, the last snowflake, the last ocean, the last life.
\par ``It's a healthy thing to think of the place of Earth among the other planets, and its place in the sun. The sun gave life and ultimately it will bring death."


\noindent 1. According to the new book, the life expectancy of the Earth is \_\_\_\_\_.\\

\noindent$\parbox[l]{0.5\paperwidth}{A. 1 billon years\\ C. 7.5 billion years}$$\parbox[l]{0.5\paperwidth}{B. 4.5 billon years\\ D. 12 billion years}$\\

\noindent2. It can be inferred from this passage that \_\_\_\_\_.\\
A. life is nothing\\
B. the world is precious\\
C. man can never conquer nature\\
D. the future of human species is gloomy\\

\noindent3. The authors of the new book believe that the human species will \_\_\_\_\_.\\
A. disapppear long before the disapperance of the Earth\\
B. survive in the universe even if the Earth disappears\\
C. find a place to live after the disappearance of the Earth\\
D. be sent into space by various spacecrafts\\

\noindent4. All of following things would come to an end before the final end of the Earth, except \_\_\_\_\_.\\

\noindent$\parbox[l]{0.5\paperwidth}{A. Mars\\ C. planets}$$\parbox[l]{0.5\paperwidth}{B. animals\\ D. oceans}$\\

\noindent5. The authors of the new book intend to tell readers primarily that \_\_\_\_\_.\\
A. the Earth is nothing but one planet in the solar system\\
B. nothing can survive for ever\\
C. we should cherish our life and environment on Earth\\
D. the sun gave life and ultimately it will bring death\\


\begin{center}
\LARGE Text 1-2
\end{center}

\par Making and selling fake copies of well-known products has been a nice little earner for crafty craftsmen over thousands of years: in Roman Gaul, unscrupulous potters would put the seals of better-known competitors on their urns so they would sell better. Until the 1980s, counterfeiting was relatively small-scale business, restricted mainly to coping luxury fashion items, such as watches and leather goods, in limited quantities. But in the 1990s it was transformed into a much bigger, broader industry, with large-scale production and distribution of false versions of such everyday items as biscuits and shampoo. Modern technology is making it ever easier to create near-perfect copies of branded goods for a fraction of the retail price of the real thing.

\par By its nature, the extent of couterfeiting is hard to measure precisely, but a study by the International Chamber of Commerce reckoned that it grew from perhaps 3$\%$ of world trade in 1990 to 5$\%$ in 1995. Jhon Pepper, chairman of Procter $\&$ Gamble, a consumer-goods multinational, says it may now be $7\%$--9$\%$, or over 450 billion a year.

\par In some developing countries, the authorities have had, at best, an \underline{ambivalent} attitude towards the booming manufacture of fake goods in their midst. After all, it creates jobs for local people and, at first sight, apperas only to hurt foreign firms. Thus the richer countries whose firms are the main victims have had to use a mixture of persuasion and threats to get poorer nations to crack down on the pirates. The Uruguay round of world trade talks, which ended in 1994, resulted in an Agreement on the Trade-Related Aspects of Intellectual-Property Rights(Trips), which obliges all member countries of the World Trade Orgnisation to impose penalties for counterfeiting and other breaches of intellectual-property rights; to enforce their piracy laws adequately; and to help firms inhibit trade in faked version of their products.

\par Besides offering poorer countries trade privileges in return for a clampdown on counterfeiting, rich countries have tried convincing them that if they try harder to enforce intellectual-property rights, they will win more foreign investment. But, realising that persuasion is having little effect, they are also resorting to threats: on January 15th, America issued a warning to the Philippines and Taiwan, two of the world's leading piracy centers, that they may have their privileges taken away unless they crack down harder on the counterfeiting gangs. Taiwan's justice minister, Chen Ding-nan, has vowed to rid the island of its reputation as pirates' den. But the counterfeiters are mocking his efforts: some pirated video discs of the new James Bond film ``Die Another Day", widely available on Taiwan's streets, carry the taunting message: ``Come and catch me, Chen Ding-nan".\\

\noindent1. The first paragraph is written to tell us that \_\_\_\_.\\
A. the history of counterfeiting is more than thousands of years \\
B. counterfeiting is an effective way to make more money \\
C. modern technology is responsible for the booming manufacture of fake goods \\
D. counterfeiting has become more and more rampant\\

\noindent2.The second paragraph is mainly about\_\_\_\_.\\
A. the extent of counterfeiting in world trade\\
B. the difficulty to measure the extent of counterfeiting\\
C. a study by the Internationam Chamber of Commerce\\
D. what John Pepper, chairman of Procter $\&$ Ganbkem says\\

\noindent3.The underlined word ambivalent" in the third paragraph most probably meas \_\_\_\_\\

\noindent$\parbox[l]{0.5\paperwidth}{A. critical\\ C. positive}$$\parbox[l]{0.5\paperwidth}{B. contradictory\\ D. negative}$\\

\noindent4. In order for poorer countries to crack down on counterfeiting, \_\_\_\_\\
A. more jobs have to be created there for local people\\
B. rich countries resort to both persuasion and threats\\
C. the World Trade Orgnisation was set up\\
D. the Uruguay round of world trade talks was held in 1994\\

\noindent5.Rich countries intend to \_\_\_\_\\
A. offer poorer countries trade privileges\\
B. take away the trade privileges they have given poorer countries\\
C. clamp down counterfeiting in poorer countries\\
D. threaten the counterfeiting gangs in Philippines and Taiwan

\begin{center}
\LARGE Text 1-3
\end{center}

\par Polluted water is nothing new in the United States. We have lived through flaming rivers and caustic creeks that could take the hide off a hound. For decades, however, efforts to safegaurd drinking water were hampered because no one had an accurate sense of the full range of contaminants in the water supply, nor of the geographic extent of the pollution. This year two separate research teams unveiled sophisticated new tools to find out exactly what chemical dangers are lurking in freshwater streams.
\par ``Research in Europe in the 1990s showed that pharmaceuticals were turing up in the water," says Dana Kolpin, leader of a U.S. Geological Survey Water Resources Division research team that developed five new analytic methods for measuring water contaminants. ``Our big effort was to develop methods to measure very small amounts of organic chemicals," The research team fanned out across 30 states nationwide and conducted two years of sampling from 139 streams. They were choson, say Kolpin, on the basis of their location downstream from ``intense urbanization and livestock production." In a study published in the March 15 Journal of Environmental Science $\&$ Technology, Kolpin and his colleagues reported they looked for 95 different contaminants, such as antibiotcs, steroids, hormones, antioxidants, plasticizers, and various solvents. They found 82 of them. Nearly 80 percent of the streams showed one or more of the contaminants. The median stream cotained seven. Even the goods news--that the most frequently detected contaminants like fecal steroids, cholesterol, inset repellent, caffeine, disinfectant, fire retardant, and deterents were found in generally low concentrations--had to be qulified. Many of those compounds have no guidelines for safe amounts, and little is known about the effects of chronic exposure or the interactive effects of compounds that have been detected together.
\par In a related Environmental Protection Agency study that is still in progress, a team of scientists at the Johns Hopkins Whiting School of Engeneering is using gas chromatography and mass spectrometry to detect the presense fo various anticonvulsants and anticancer drugs in drinking water. Led by Lynn Roberts and Ed Bouwer, the researcher track samples at sewagetreatment facilities in Massachusetts and Maraland to determine whether and in what quantities pharmaceuticals are getting through the waste-treatment plants and the extent to which they may be accumulating in coastal waters.
\par The goal of both research teams is to provide a baseline of what organic compunds are in the water, in what quantities, and how they are getting there-- key steps towards ensuring that the water we drink isn't killing us.

\noindent 1. The second sentence of the first paragraphy, "We have lived through...off a hound", intends to say that\_\_\_\_.\\
A. many rivers and creeks have been excessively polluted by various contaminants.\\
B. our lives depend on flaming rivers and caustic creeks\\
C. we cannt prevent rivers and creeks from being hounded\\
D. people cannot live without the supply of water from rivers and creeks.\\
\noindent 2. According to this passage, two research teams\_\_\_\_.\\
A. have determined the full geographic extent of the water supply\\
B. have ascertained the geographic extent of the water pollution\\
C. have developed new methods to measure water contaminants\\
D. have succeeded in preventing drinking water from being polluted\\
\noindent 3.Which of the following statements is true?\\
A. Altogether 95 different contaminants have been found in streams.\\
D. Nearly 80 percent of the streams surveyed contains only the familiar contaminants.\\
C. The most frequently detected contaminants are usually in low concentrations.\\
D. The average number of the contaminants in each stream surveyed in seven.\\
\noindent 4. The two research teams mentioned in the passage endevor\_\_\_\_.\\
A. to track samples at more sewage-treatment facilities\\
B. to determine latent chemical dangers in the water\\
C. to measure the exact amount of any drug found in drinking water\\
D. to find out the precise number of contaminants in freshwater streams\\
\noindent 5. Which of the following can serve as the best title of the passage?\\
A. The organic Compounds in the Water\\
B. Drinking water drugged\\
C. Polluted Rivers and Streams\\
D. Guidelines for safe water\\ 


\begin{center}
\LARGE Text 1-4
\end{center}

\par Experiments on monkeys were viewed much more negatively than those involving mice. Indeed, only experiments to test or develop drugs to treat childhood leukaemia were seen as justifying monkeys suffering. In Britain, experiments involving primates are very tightly controlled. Researchers must convince goverment officials that the knownledge to be gained justifies any suffering to the animals, and that adequate data cannot be obtained by using other species.
\par In practice, this means that monkeys are unlikely to be used in leukaemia research, as the disease can be studied in other animals. But attempts to develop AIDS vaccines depend heavily on experiments with related viruses in monkeys, in which some of the animals are likely to become ill. Our poll indicates that a majority of British people would oppose these experiments.
\par In the US, where regulations are less stringent, the goal of developing an AIDS vaccine is seen as sufficient justification for injecting chimpanzees, our nearest relatives, with potentially lethal strains of HIV. And while most people are probaly not aware of such facts, 64 per cent of those we polled judged correctly that regulations governing animal experiments in Britain are as strict, or stricter, than those in other developed contries. Just 11 per cent thought that British rules are less strict, while 24 per cent said they didn't known.
\par In one respect, however, our poll reveals a disturbing gap in people's knownledge, which the British government might want to address. No prescription drug is marketed without first being tested in animals, yet people are either unaware that this is the case, or don't want to acknownledge the fact. While 35 per cent of the people we polled-said they or a close family member had been prescribed a drug for a serious illness in the past two years or so, only 18 per cent of these people-6 per cent of the total samples-knew it had been tested on animals. Signficantly, this small group was more favourably disposed to animals experiments than the larger number who said they weren't aware their drugs had been tested on animals. Indeed, with 66 per cent of  them backing animal research in our question, they were more positive about animals experiments than everyone we polled except the hunters and fur wearers.
\par While people may not be in full possession of the facts about animal research, many experiments that are licensed in Britain--including hundreds of thousands of toxicity tests and fundamental biological studies--could be banned if regulators were to follow the majority views expressed in our poll.
\par People can clearly weigh the pros and cons of animal exprimentation. It's time for those who want to pursue a peaceful debate to seize the initiative.
\noindent 1.Most people ingore the fact that\_\_\_\_\\
A. no new drugs would ever be developed without monkeys being involved.\\
B. all the prescription drugs sold on market have been tested on animals\\
C. leukaemia can hardly be studied in animals other than monkeys\\
D. adequate data can still be obtained without using monkeys in animal research\\
\noindent 2. In the U.S., it is believed that\_\_\_\_\\
A. monkeys can be involved in the experimentation to develop an AIDS vaccine\\
B. to test petential lethal drugs on animals isn't justifiable in any case\\
C. Animal research is justified only if it helps us gain new knownledge\\
D. the regulations governing animal research should be less strict\\

\noindent 3. According to this passage, \_\_\_\_ of those being polled were aware that the drug they had been prescribed had been tested on animals.\\

\noindent$\parbox[l]{0.5\paperwidth}{A. 6$\%$\\ C. 35$\%$}$$\parbox[l]{0.5\paperwidth}{B. 18$\%$\\ D. 66$\%$}$\\

\noindent 4. We can learn from this passage, \_\_\_\_ may be negative about animal experimentation.\\
A. the hunters and fur coat wearers\\
D. those who support animal research\\
C. those who are unaware that their drugs had been tested on animals\\
D. those who are in full possession of the facts about animal research\\
\noindent 5. The author's attitude towards animal experimentation is \_\_\_\_\\

\noindent$\parbox[l]{0.5\paperwidth}{A. negative\\C. subjective}\parbox[l]{0.5\paperwidth}{B. positive\\D. objective}$\\


\end{document}
